---
title: "p8105_hw1_st3431_"
author: "Supraja Teki"
output: github_document
date: "2022-09-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

## Problem 1

```{r description}
data("penguins", package = "palmerpenguins")

summary(penguins)
  summary(penguins$flipper_length_mm)
  summary(penguins$species)

nrow(penguins)

ncol(penguins)

mean(penguins$flipper_length_mm, na.rm=T)

```

```{r scatterplot}
plot_df=
  tibble(
    x=penguins$bill_length_mm,
    y=penguins$flipper_length_mm
  )
  
ggplot(plot_df, aes(color=penguins$species, x = x, y = y)) + geom_point()
```

## Problem 2

```{r}
hw_df=tibble(random_sample=rnorm(10), 
  vec_logic=random_sample>0, 
  vec_character=c("a","b","c","d","e","f","g","h","i","j"), 
  vec_factor=factor(c("low", "medium", "high", "low","medium","high", "low","medium","high","low")) )

#means of variable within the df
  mean(hw_df$vec_logic)
  mean(hw_df$vec_character)
  mean(hw_df$vec_factor)
  mean(hw_df$random_sample)
```

Running the means of the character and factor variables did not work because a character vector is a string of letters which means a numeric mean cannot be taken, while the factor variable is also categorical and so the mean cannot be taken.  

```{r, eval=FALSE}
as.numeric(hw_df$vec_logic)
as.numeric(hw_df$vec_character)
as.numeric(hw_df$vec_factor)
```

After applying the as.numeric the variables were given number values but they were set values of 1, 2, or 3. This happens because the variables were forced to assign numeric values to categorical variables.   


